\thetitle

### 2021-02-22 writing/landscape.tex
space war

All three systems used here are implemented on top of the common basis of
Racket. The use the Typed Racket syntax and type checker for all three
semantics. The Natural semantics is inherited as is, while the Erasure semantics
is the one of plain Racket.  The Transient system implements the design
of~\citet{vss-popl-2017}, though constructing it demands two design decisions:
which shallow checks to use and where, plus how to maintain a blame map in a
full-fledged run-time system.

@@

Once the type checker has completed its work, Transient translates the source
into an alternative form and in the process inserts run-time checks. Technically
speaking, the rewriting pass wraps all elimination in applications of shallow
checks.  For example, if the variable {\tt f} has the static type {\tt (->
String String)}, the application {\tt (f x)} must be rewritten to check for a
string result because {\tt f} could be an untyped function.

>>>>

All three systems used for the experiment are variants of Racket. The
use the Typed Racket syntax and type checker for all three
semantics. The Natural semantics is inherited as is, while the Erasure
semantics is the one of plain Racket.  The Transient system implements
the design of~\citet{vss-popl-2017}, though constructing it demands
two design decisions: which shallow checks to use and where, plus how
to maintain a blame map in a full-fledged run-time system.

@@

Once the type checker has completed its work, Transient rewrites the
source to insert run-time checks. Technically speaking, the rewriting
pass wraps all elimination in applications of shallow checks.  For
example, if the variable {\tt f} has the static type {\tt (-> String
String)}, the application {\tt (f x)} must be rewritten to check for a
string result because {\tt f} could be an untyped function.
